### 2016-09-19 doc/manual/version3/inputParameters.tex
adding more magnetic drift options

{\ttfamily magneticDriftScheme} = 4: Magnetic drift as defined in
Eq.~(16) in \cite{Martitsch2016}. (This only works for .bc magnetic
geometry input files so far)\\

>>>>

{\ttfamily magneticDriftScheme} = 4: Magnetic drift as defined in
Eq.~(16) in \cite{Martitsch2016}.\\ (This {\ttfamily
  magneticDriftScheme} only works for .bc magnetic
geometry input files so far)\\

{\ttfamily magneticDriftScheme} = 5: Magnetic drift as defined in
Eqs.~(46--48) in \cite{Sugama2016}. The function $\alpha$
 is chosen as $\alpha=(1-\xi^2)/(1+\xi^2)$ for the terms
in Eq.~(48) proportional to the normal curvature, which are the terms
that need
to be regularized at $\xi=\pm 1$.\\
(This {\ttfamily magneticDriftScheme} only works for .bc magnetic
geometry input files so far)\\
